FinalManuscript_DISCS_UG

### 2019-03-04 parts/02_relatedliterature_04homomorphiccryptosystems.tex
Done with first pass of sections 2.1 to 2.3 of RRL
Note: linebreaking in URLs in section 2.3 have to be addressed
Cleaned up definition of cryptosystems in Ch2

Now that we've established the image processing operations we wish to implement, we now discuss the homomorphic cryptosystems we will be using to implement privacy-preserving image processing.

A cryptosystem consists of an encryption function $\mathcal{E}$ and a decryption function $\mathcal{D}$, along with the plaintext space $\mathcal{P}$, ciphertext space $\mathcal{C}$ and the key space $\mathcal{K}$~\cite{bauer_cryptosystem_2005}. A \textit{plaintext} is text that can be commonly understood, while a \textit{ciphertext} results from encrypting the plaintext using an encryption key. The \textit{plaintext space} is the set of all possible plaintexts, the \textit{ciphertext space} is the set of all possible ciphertexts, while the \textit{keyspace} is the set of all possible keys.

There are two kinds of cryptosystems, \textit{symmetric} and \textit{asymmetric}. In symmetric-key cryptosystems, the same key is used for both encryption and decryption. As a consequence, symmetric-key cryptosystems must be implemented with a secure key exchange protocol, so that both the sender and receiver have access to the same key. Prominent examples of symmetric-key cryptosystems are the Data Encryption Standard (DES), and its replacement, the Advanced Encryption Standard (AES).

On the other hand, asymmetric-key (or public-key) cryptosystems use separate keys for encryption and decryption. The encryption key (also called the \textit{public key}) is shared publicly, while the decryption key (also called the \textit{private key}) is kept secret. Since the public key and private keys are different, there is no need to agree upon secure key exchange protocols. Usually, the security of asymmetric-key cryptosystems relies on the intractability of certain computational problems, for example, the RSA cryptosystem depends on the difficulty of big integer factorization~\cite{rivest_method_1978}, while the ElGamal cryptosystem depends on the difficulty of the discrete logarithm problem~\cite{blakley_public_1985}.

Homomorphic cryptosystems are a special type of cryptosystem in which operations can be securely performed on encrypted data. Suppose that for a public-key cryptosystem, $\mathcal{E}_k \left(p \right)$ is the encryption function using the public key $k \in \mathcal{K}$, and $\mathcal{D}_l \left(c \right)$ be the decryption function using the private key $l$. A cryptosystem is said to be homomorphic if its encryption function is homomorphic, that is, if it satisfies the relation
\begin{equation}
    \mathcal{E}_k \left(p_1 \boxplus p_2\right) = \mathcal{E}_k \left(p_1\right) \boxdot \mathcal{E}_k \left(p_2\right)
\end{equation}
where $p_1, p_2 \in \mathcal{P}$ are the plaintexts, and $\boxplus$ and $\boxdot$ are operations in $\mathcal{P}$ and $\mathcal{C}$ respectively~\cite{fontaine_survey_2007}. Furthermore, a homomorphic cryptosystem also satisfies~\cite{li_elliptic_2012}
\begin{equation}
    p_1 \boxplus p_2 = \mathcal{D}_l \left( \mathcal{E}_k \left(p_1\right) \boxdot \mathcal{E}_k \left(p_2\right) \right).
\end{equation}
In other words, a homomorphic cryptosystem preserves the operations that can be done with the plaintext without requiring an intermediary step of decrypting the ciphertext beforehand. It is important to note that the operations $\boxplus$ and $\boxdot$ need not be the same. A simple operation in the plaintext space may require a computationally intensive operation in the ciphertext space.

Homomorphic cryptosystems can be classified according to the plaintext and ciphertext operations, $\boxplus$ and $\boxdot$. If the plaintext operation $\boxplus$ is addition, the cryptosystem is said to be \textit{additively homomorphic}, and the cryptosystem is said to be \textit{multiplicatively homomorphic} if the plaintext operation $\boxplus$ is multiplication.

>>>>

A cryptosystem~\cite{bauer_cryptosystem_2005} consists of an encryption function $\mathcal{E}$ and a decryption function $\mathcal{D}$, which operate on three sets: the plaintext space $\mathcal{P}$, ciphertext space $\mathcal{C}$ and the key space $\mathcal{K}$ A \textit{plaintext}, an element of the \textit{plaintext space}, is text that can be commonly understood within a larger group. Given a \textit{key}, an element of the \textit{key space}, the encryption function maps a plaintext to some \textit{ciphertext}, an element of the ciphertext space which can only be understood by authorized parties. The decryption function similarly maps a ciphertext back to its corresponding plaintext, given an appropiate key. By sending data as ciphertext and only exposing the corresponding plaintexts to authorized parties who have access to the appropiate keys, secure data transmission can be achieved.

Cryptosystems may be classified as either \textit{symmetric} or \textit{asymmetric}. 
In symmetric-key cryptosystems, the same key is used for both encryption and decryption. As a consequence, symmetric-key cryptosystems must be implemented with a secure key exchange protocol, so that both the sender and receiver have access to the same key while keeping the key secret. 
Prominent examples of symmetric-key cryptosystems are the Data Encryption Standard (DES), and its replacement, the Advanced Encryption Standard (AES).

On the other hand, asymmetric-key (or public-key) cryptosystems use separate keys for encryption and decryption. The encryption key (also called the \textit{public key}) is shared publicly, while the decryption key (also called the \textit{private key}) is kept secret. Since the public key and private keys differ, secure key exchange protocols are not required. The security of asymmetric-key cryptosystems rely on the intractability of certain computational problems, for example, the RSA cryptosystem depends on the difficulty of big integer factorization~\cite{rivest_method_1978}, while the ElGamal cryptosystem depends on the difficulty of the discrete logarithm problem~\cite{blakley_public_1985}.

Homomorphic cryptosystems are a special type of cryptosystem in which operations can be securely performed on encrypted data. Suppose that in a public-key cryptosystem, $\mathcal{E}_k \left(p \right)$ is the encryption function which uses a public key $k$, and $\mathcal{D}_l \left(c \right)$ be the decryption function which uses a private key $l$. The cryptosystem is said to be homomorphic if its encryption function is homomorphic, that is, if it satisfies the relation
\begin{equation}
    \label{eq:homomorphic_definition_encryption}
    \mathcal{E}_k \left(p_1 \boxplus p_2\right) = \mathcal{E}_k \left(p_1\right) \boxdot \mathcal{E}_k \left(p_2\right)
\end{equation}
where $p_1, p_2 \in \mathcal{P}$ are plaintexts, and $\boxplus$ and $\boxdot$ are operations in $\mathcal{P}$ and $\mathcal{C}$ respectively~\cite{fontaine_survey_2007}. By applying the decryption function $\mathcal{D}_l$ to both sides of equation~\ref{eq:homomorphic_definition_encryption}, we can see that a homomorphic cryptosystem also satisfies~\cite{li_elliptic_2012}
\begin{equation}
    \label{eq:homomorphic_definition_decryption}
    p_1 \boxplus p_2 = \mathcal{D}_l \left( \mathcal{E}_k \left(p_1\right) \boxdot \mathcal{E}_k \left(p_2\right) \right).
\end{equation}
In other words, a homomorphic cryptosystem allows operations to be performed on recovered plaintexts by performing corresponding operations on ciphertexts. Using a homomorphic cryptosystem, secure computation can be achieved by encrypting plaintexts and then operating on the ciphertexts. We note that the operations $\boxplus$ and $\boxdot$ need not be the same. A simple operation in the plaintext space may require a computationally intensive operation in the ciphertext space.

Homomorphic cryptosystems can be classified according to the supported plaintext operation(s) $\boxplus$ which can be securely computed. The cryptosystem is said to be \textit{additively homomorphic} if the plaintext operation $\boxplus$ is addition, and the cryptosystem is said to be \textit{multiplicatively homomorphic} if the plaintext operation $\boxplus$ is multiplication. Homomorphic cryptosystems which only allow for a limited set of operations to be computed securely are called \textit{partially homomorphic} while those which allow for arbitrary operations to be computed securely are called \textit{fully homomorphic}. Numerous partially homomorphic and fully homomorphic cryptosystems have been developed in the literature. This study will compare several of them, which we will now introduce in detail.
